Impact of Molecular Subtype on Inflammatory Breast Cancer-Specific Mortality in Adult Women

### 2024-12-03 products/manuscript/manuscript.qmd
tibbles 1 and 2

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	error = FALSE,
	knitr.graphics.error = FALSE
)
library(yaml, include.only = NULL)
library(knitr, include.only = NULL)
library(here)

@@

```{r}
#| label: tbl-table1
#| tbl-cap: |
#|   [Clinicopathological characteristics by cancer subtype]{color="#FF2400"}
#| echo: false

knitr::include_graphics(
	here::here("results", "tables", "t1.rds")
)
```

@@

```{r}
#| label: tbl-table2
#| tbl-cap: |
#|   [Schoenfeld Residual and Ranked Survival Time Correlation]{color="#FF2400"}
#| out.width: 40%
knitr::include_graphics(
	here::here("results", "tables", "t2.png")
)
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	error = FALSE,
	knitr.graphics.error = FALSE
)
library(yaml, include.only = NULL)
library(knitr, include.only = NULL)
library(here)
library(flextable)

@@

```{r}
#| label: tbl-table1
#| tbl-cap: |
#|   [Clinicopathological characteristics by cancer subtype]{color="#FF2400"}
#| echo: false
#| results: asis

t1 <- readRDS(file = here::here("results/tables", "t1.rds"))
t1

```

@@

```{r}
#| label: tbl-table2
#| tbl-cap: |
#|   [Schoenfeld Residual and Ranked Survival Time Correlation]{color="#FF2400"}
#| echo: false
#| results: asis

t2 <- readRDS(file = here::here("results/tables", "t2.rds"))
t2
```
